---
title: "TSS-Stress_Debrief_V_TSS-Stress_20210125"
output:
  html_document: 
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Clean Enviorment
```{r, echo=FALSE, warning=FALSE}

#Clear environemnt and Load Packages

# clear the environment
rm(list=ls()) 

#detach("package:here", unload = TRUE)

if (!require("pacman")) install.packages("pacman")
 pacman::p_load(
   plyr,  # For join function
   tidyverse, #for dyplr functions
   here # for setting path and working directory
   )
```

#Set Working Directory and Paths 
```{r, echo=FALSE, warning=FALSE}

# set the Working Directory and paths 
here()
# set seed
set.seed(42) 
# set directory
setwd(here())
# import data

#set version 
curVersion="TSS-Stress_20210125"
curDate=Sys.Date()

path.raw.data= "../../../../../Data/QualtricsSRMS/TSS-Stress_20210125/RawData/TSS-Stress-Debrief_January+31,+2021_11.32.csv"

path.clean.data = paste0("../../../../../Data/QualtricsSRMS/",curVersion,"/CleanedData/TSS-Stress_Debrief_Clean_Version_",curVersion,"_Date_",curDate,".csv", sep = "")


ProlificLogPath=paste0("../../../../../Participants/",curVersion,"/Prolific/")


SONA_PAYLogPath=paste0("../../../../../Participants/",curVersion,"/SONA_PAY/")
SONA_CREDITLogPath=paste0("../../../../../Participants/",curVersion,"/SONA_CREDIT/")


```

#Import Raw Data
```{r, echo=FALSE, warning=FALSE}

#import raw data

data.raw = read.csv(file = path.raw.data,header=TRUE,na.strings="")



prolificFiles = list.files(path=ProlificLogPath, pattern="*.csv", full.names=TRUE)
data.prolific = ldply(prolificFiles, read_csv)

Sona_PayFiles = list.files(path=SONA_PAYLogPath, pattern="*.csv", full.names=TRUE)
data.SonaPay = ldply(Sona_PayFiles, read_csv)

Sona_CreditFiles = list.files(path=SONA_CREDITLogPath, pattern="*.csv", full.names=TRUE)
data.SonaCredit = ldply(Sona_CreditFiles, read_csv)



#data.Error = read.csv(file = ErrorLogPath,header=TRUE,na.strings="NaN")
```


#Filter Sona and Prolific Participant logs by Approved (PROLIFIC) and Participated (SONA)
<!--This does not yet filter out people who might have had errors or messaged the researcher-->

```{r, echo=FALSE, warning=FALSE}


if(length(data.SonaCredit!=0))(
data.Sona.filter<- data.Sona %>%
   dplyr::select(survey_id,credit_type)%>%
   dplyr::filter(credit_type=="Participated")%>%
    dplyr::select(survey_id)%>%
    distinct(participant_id)
)

if(length(data.SonaPay!=0))(
data.SonaPay.filter<- data.SonaPay %>%
   #dplyr::select(survey_id,credit_type)%>%
   dplyr::filter(credit_type=="Participated")%>%
    #dplyr::select(survey_id)%>%
    distinct(survey_id)%>%
    rename(SubID=survey_id)
)

if(length(data.prolific!=0))(

data.prolific.filter<- data.prolific %>%
   dplyr::select(participant_id,status)%>%
   dplyr::filter(status=="APPROVED")%>%
    dplyr::select(participant_id)%>%
    distinct(participant_id)%>%
    rename(SubID=participant_id)
)

# data.Independent<- data.raw%>%
#   filter(PLATFORM=="INDEPENDENT")%>%
#   select(INDEPENDENT_PID)%>%
#   distinct(INDEPENDENT_PID)%>%
#     rename(SubID=INDEPENDENT_PID)

data.SubjectListCombined<- data.prolific.filter
#data.SubjectListCombined<- join(data.prolific.filter, data.SonaPay.filter,type= "full")
#data.SubjectListCombined<- join(data.SubjectListCombined,data.Independent,type= "full")
```





#Filter Raw Data by Study Version
```{r, echo=FALSE, warning=FALSE}

data.filter<- data.raw %>%
   dplyr::filter(AssignmentID==curVersion)#%>%
 # dplyr::filter(PROLIFIC_PID %in%data.Error$PROLIFIC_PID)

```


#Filter Raw Data by IDs in prolific and sona subject logs
```{r, echo=FALSE, warning=FALSE}

data.filter<- data.filter %>%
# dplyr::filter(workerId %in%data.prolific.filter$participant_id |SubID %in%data.Sona.filter$survey_id ) 
  dplyr::filter(WorkerID %in%data.SubjectListCombined$SubID ) 
```


## Embedded Data Information
```{r , echo=FALSE}
data.Embedded=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,bP,order)

```


## Difficulty Cues
<!-- Scored on a 12 point scale -->

<!-- Composite_Collector_PosLPenL_7 & Composite_Collector_PosLPenH_7:Like -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Composite_Collector_PosLPenL_1 & Composite_Collector_PosLPenH_1:Pleasant -5 unpleasant/negative = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 pleasant/positive= 5 Prefer not to respond =NA -->

<!-- Composite_Collector_PosLPenL_2 & Composite_Collector_PosLPenH_2:Arousal -5 relaxed/calm = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 stimulated/aroused= 5 Prefer not to respond =NA -->

<!-- Composite_Collector_PosLPenL_3 & Composite_Collector_PosLPenH_3:Motivation -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Composite_Collector_PosLPenL_4 & Composite_Collector_PosLPenH_4:Difficult -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Composite_Collector_PosLPenL_5 & Composite_Collector_PosLPenH_5:Effort -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->


<!-- Composite_Collector_PosLPenL_6 & Composite_Collector_PosLPenH_6:Attention -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

### Low Difficulty Cue
```{r, echo=FALSE, warning=FALSE}

# recode data
data.EasyCue=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,starts_with("Composite_Collector_PosLPenL"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("Composite_Collector_PosLPenL_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.EasyCue<-data.EasyCue %>%
  rename(Easy_Like= Composite_Collector_PosLPenL_7, #7
         Easy_Pleasant= Composite_Collector_PosLPenL_1, #1
         Easy_Arousal= Composite_Collector_PosLPenL_2, #2
         Easy_Motivation= Composite_Collector_PosLPenL_3, #3
         Easy_Difficult= Composite_Collector_PosLPenL_4, #4
         Easy_Effort= Composite_Collector_PosLPenL_5, #5
         Easy_Attention= Composite_Collector_PosLPenL_6) #6
  

  
```

### High Difficulty Cue
```{r, echo=FALSE, warning=FALSE}

# recode data
data.HardCue=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,starts_with("Composite_Collector_PosLPenH_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("Composite_Collector_PosLPenH_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.HardCue<-data.HardCue %>%
  rename(Hard_Like= Composite_Collector_PosLPenH_7, #7
         Hard_Pleasant= Composite_Collector_PosLPenH_1, #1
         Hard_Arousal= Composite_Collector_PosLPenH_2, #2
         Hard_Motivation= Composite_Collector_PosLPenH_3, #3
         Hard_Difficult= Composite_Collector_PosLPenH_4, #4
         Hard_Effort= Composite_Collector_PosLPenH_5, #5
         Hard_Attention= Composite_Collector_PosLPenH_6) #6
  

  
```



## Reward Cues (GEMS)
<!-- Scored on a 12 point scale -->

<!-- LowGem_7 & HighGem_7:Like -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- LowGem_1 & HighGem_1:Pleasant -5 unpleasant/negative = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 pleasant/positive= 5 Prefer not to respond =NA -->

<!-- LowGem_2 & HighGem_2:Arousal -5 relaxed/calm = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 stimulated/aroused= 5 Prefer not to respond =NA -->

<!-- LowGem_3 & HighGem_3:Motivation -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- LowGem_4 & HighGem_4:Difficult -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- LowGem_5 & HighGem_5:Effort -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->


<!-- LowGem_6 & HighGem_6:Attention -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

### Low Reward Cue
```{r, echo=FALSE, warning=FALSE}

# recode data
data.LowRewardCue=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,starts_with("LowGem_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("LowGem_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.LowRewardCue<-data.LowRewardCue %>%
  rename(Easy_Like= LowGem_7, #7
         Easy_Pleasant= LowGem_1, #1
         Easy_Arousal= LowGem_2, #2
         Easy_Motivation= LowGem_3, #3
         Easy_Difficult= LowGem_4, #4
         Easy_Effort= LowGem_5, #5
         Easy_Attention= LowGem_6) #6
  

  
```

### High Reward Cue
```{r, echo=FALSE, warning=FALSE}

# recode data
# recode data
data.HighRewardCue=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,starts_with("HighGem_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("HighGem_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.HighRewardCue<-data.HighRewardCue %>%
  rename(Easy_Like= HighGem_7, #7
         Easy_Pleasant= HighGem_1, #1
         Easy_Arousal= HighGem_2, #2
         Easy_Motivation= HighGem_3, #3
         Easy_Difficult= HighGem_4, #4
         Easy_Effort= HighGem_5, #5
         Easy_Attention= HighGem_6) #6

  
```


## Feedback
<!-- Scored on a 12 point scale -->

<!-- Q261_15_4 & Q261_14_4:Like -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Q261_15_1 & Q261_14_1:Motivation -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Q261_15_2 & Q261_14_2:Difficult -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Q261_15_3 & Q261_14_3:Attention -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->


### Easy Feedback - Goal Reached
```{r, echo=FALSE, warning=FALSE}

# recode data
data.EasyReachedFB=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,Q261_15_1,Q261_15_2,Q261_15_3,Q261_15_4)%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  dplyr::mutate_at(vars(starts_with("Q261_15_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.EasyReachedFB <-data.EasyReachedFB %>%
  rename(EasyReachedFB_Like=Q261_15_4,
         EasyReachedFB_Motivation= Q261_15_1,
         EasyReachedFB_Difficult= Q261_15_2,
         EasyReachedFB_Attention= Q261_15_3)
  
```

### Easy Feedback - Goal failed
```{r, echo=FALSE, warning=FALSE}

# recode data
data.EasyFailedFB=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,Q261_14_1,Q261_14_2,Q261_14_3,Q261_14_4)%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  dplyr::mutate_at(vars(starts_with("Q261_14_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.EasyFailedFB <-data.EasyFailedFB %>%
  rename(EasyFailedFB_Like=Q261_14_4,
         EasyFailedFB_Motivation= Q261_14_1,
         EasyFailedFB_Difficult= Q261_14_2,
         EasyFailedFB_Attention= Q261_14_3)
  
```

### Hard Feedback - Goal Reached
```{r, echo=FALSE, warning=FALSE}

# recode data
data.HardReachedFB=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,Q261_15_1.1,Q261_15_2.1,Q261_15_3.1,Q261_15_4.1)%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  dplyr::mutate_at(vars(starts_with("Q261_15_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.HardReachedFB <-data.HardReachedFB %>%
  rename(HardReachedFB_Like=Q261_15_4.1,
         HardReachedFB_Motivation= Q261_15_1.1,
         HardReachedFB_Difficult= Q261_15_2.1,
         HardReachedFB_Attention= Q261_15_3.1)
  
```
### Hard Feedback - Goal failed
```{r, echo=FALSE, warning=FALSE}

# recode data
data.HardFailedFB=data.filter %>%
  dplyr::select(WorkerID,PLATFORM,Q261_14_1.1,Q261_14_2.1,Q261_14_3.1,Q261_14_4.1)%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  dplyr::mutate_at(vars(starts_with("Q261_14_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.HardFailedFB <-data.HardFailedFB %>%
  rename(HardFailedFB_Like=Q261_14_4.1,
         HardFailedFB_Motivation= Q261_14_1.1,
         HardFailedFB_Difficult= Q261_14_2.1,
         HardFailedFB_Attention= Q261_14_3.1)
  
```


## Merge data

```{r, echo=FALSE}


#merge all of the cleaned data files 

data.cleanDebrief <-data.Embedded %>%
  join(data.EasyCue,by=c("WorkerID","PLATFORM") ) %>%
  join(data.HardCue,by=c("WorkerID","PLATFORM") ) %>%
  join(data.LowRewardCue,by=c("WorkerID","PLATFORM") ) %>%
  join(data.HighRewardCue,by=c("WorkerID","PLATFORM") ) %>%
  join(data.EasyReachedFB,by=c("WorkerID","PLATFORM") ) %>%
  join(data.EasyFailedFB,by=c("WorkerID","PLATFORM") ) %>%
  join(data.HardReachedFB,by=c("WorkerID","PLATFORM") ) %>%
  join(data.HardFailedFB,by=c("WorkerID","PLATFORM") )
 
write.csv(data.cleanDebrief,path.clean.data, row.names = FALSE)





```


