---
title: "TSS-Stress_Cleaning_V_TSS-Stress_20210125"
output:
  html_document: 
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Clean Enviorment
```{r, echo=FALSE, warning=FALSE}

#Clear environemnt and Load Packages

# clear the environment
rm(list=ls()) 

#detach("package:here", unload = TRUE)

if (!require("pacman")) install.packages("pacman")
 pacman::p_load(
   plyr,  # For join function
   tidyverse, #for dyplr functions
   here # for setting path and working directory
   )
```

#Set Working Directory and Paths 
```{r, echo=FALSE, warning=FALSE}

# set the Working Directory and paths 
here()
# set seed
set.seed(42) 
# set directory
setwd(here())
# import data

#set version 
curVersion="TSS-Stress_20210125"
curDate=Sys.Date()

path.raw.data= "../../../../../Data/QualtricsSRMS/TSS-Stress_20210125/RawData/TSS-Stress-SRMS_March+9,+2021_21.14.csv"

path.clean.data = paste0("../../../../../Data/QualtricsSRMS/",curVersion,"/CleanedData/TSS-Stress_SRMS_Clean_Version_",curVersion,"_Date_",curDate,".csv", sep = "")


ProlificLogPath=paste0("../../../../../Participants/",curVersion,"/Prolific/")


SONA_PAYLogPath=paste0("../../../../../Participants/",curVersion,"/SONA_PAY/")
SONA_CREDITLogPath=paste0("../../../../../Participants/",curVersion,"/SONA_CREDIT/")


```

#Import Raw Data
```{r, echo=FALSE, warning=FALSE}

#import raw data

data.raw = read.csv(file = path.raw.data,header=TRUE,na.strings="")



prolificFiles = list.files(path=ProlificLogPath, pattern="*.csv", full.names=TRUE)
data.prolific = ldply(prolificFiles, read_csv)

Sona_PayFiles = list.files(path=SONA_PAYLogPath, pattern="*.csv", full.names=TRUE)
data.SonaPay = ldply(Sona_PayFiles, read_csv)

Sona_CreditFiles = list.files(path=SONA_CREDITLogPath, pattern="*.csv", full.names=TRUE)
data.SonaCredit = ldply(Sona_CreditFiles, read_csv)



#data.Error = read.csv(file = ErrorLogPath,header=TRUE,na.strings="NaN")
```


#Filter Sona and Prolific Participant logs by Approved (PROLIFIC) and Participated (SONA)
<!--This does not yet filter out people who might have had errors or messaged the researcher-->

```{r, echo=FALSE, warning=FALSE}


if(length(data.SonaCredit!=0))(
data.Sona.filter<- data.Sona %>%
   dplyr::select(survey_id,credit_type)%>%
   dplyr::filter(credit_type=="Participated")%>%
    dplyr::select(survey_id)%>%
    distinct(participant_id)
)

if(length(data.SonaPay!=0))(
data.SonaPay.filter<- data.SonaPay %>%
   #dplyr::select(survey_id,credit_type)%>%
   dplyr::filter(credit_type=="Participated")%>%
    #dplyr::select(survey_id)%>%
    distinct(survey_id)%>%
    rename(SubID=survey_id)
)

if(length(data.prolific!=0))(

data.prolific.filter<- data.prolific %>%
   dplyr::select(participant_id,status)%>%
   dplyr::filter(status=="APPROVED")%>%
    dplyr::select(participant_id)%>%
    distinct(participant_id)%>%
    rename(SubID=participant_id)
)

data.Independent<- data.raw%>%
  filter(PLATFORM=="INDEPENDENT")%>%
  select(INDEPENDENT_PID)%>%
  distinct(INDEPENDENT_PID)%>%
    rename(SubID=INDEPENDENT_PID)

data.SubjectListCombined<- data.prolific.filter
#data.SubjectListCombined<- join(data.prolific.filter, data.SonaPay.filter,type= "full")
#data.SubjectListCombined<- join(data.SubjectListCombined,data.Independent,type= "full")
```





#Filter Raw Data by Study Version
```{r, echo=FALSE, warning=FALSE}

data.filter<- data.raw %>%
   dplyr::filter(Version==curVersion)#%>%
 # dplyr::filter(PROLIFIC_PID %in%data.Error$PROLIFIC_PID)

```


#Create Subject ID to use that contains all IDS
```{r echo=FALSE}

# data.filter<- data.filter %>%
#   dplyr::mutate(SubID=case_when(
#     !is.na(INDEPENDENT_PID)~INDEPENDENT_PID,
#     !is.na(PROLIFIC_PID)~PROLIFIC_PID,
#     !is.na(SONA_PID)~SONA_PID,
# 
#     )
#   )
data.filter<-data.filter %>% dplyr::mutate(SubID=coalesce(INDEPENDENT_PID,PROLIFIC_PID,SONA_PID))
```



#Filter Raw Data by IDs in prolific and sona subject logs
```{r echo=FALSE, warning=FALSE}

data.filter<- data.filter %>%
 dplyr::filter(SubID %in%data.SubjectListCombined$SubID ) 
```



#Duration in minutes
```{r, echo=FALSE, warning=FALSE}

data.duration<- data.filter %>%
  dplyr::select(SubID,PLATFORM, starts_with("Duration")) %>%
  dplyr::mutate_at(vars(starts_with("Duration")),as.character)%>%
  dplyr::mutate_at(vars(starts_with("Duration")),as.numeric)%>%
  dplyr::mutate(durationSRMS= ((Duration..in.seconds.)/60))

data.durationSONA<- data.filter %>%
  dplyr::select(SubID,PLATFORM, starts_with("Duration")) %>%
  dplyr::filter(PLATFORM=="SONA_PAY")%>%
  dplyr::mutate_at(vars(starts_with("Duration")),as.character)%>%
  dplyr::mutate_at(vars(starts_with("Duration")),as.numeric)%>%
  dplyr::mutate(durationSRMS= ((Duration..in.seconds.)/60))

data.durationProlific<- data.filter %>%
  dplyr::select(SubID,PLATFORM, starts_with("Duration")) %>%
  dplyr::filter(PLATFORM=="PROLIFIC")%>%
  dplyr::mutate_at(vars(starts_with("Duration")),as.character)%>%
  dplyr::mutate_at(vars(starts_with("Duration")),as.numeric)%>%
  dplyr::mutate(durationSRMS= ((Duration..in.seconds.)/60))




  
```



## Eligibility Check

<!--Elig_ColorBlindness: Yes=0, No=1,No, I have red-green color blindness=1, No, I have blue-yellow color blindness=1, Prefer not to respond= NA-->
<!--Elig_Dyslexic= Yes=1, No=0 -->
<!--Elig_NormalVision: Normal Vision=0, 	Corrected Vision=0, Non Corrected Vision=1, Prefer not to respond= NA	 -->
<!--Elig_NativeEnglish: Yes=0, No=1, No, but I am fluent=.5,Prefer not to respond= NA -->

```{r , echo=FALSE}



#select Questions about eligibility 
data.Eligibility=data.filter %>%
  dplyr::select(SubID,PLATFORM, Q25, Q27, Q31, Q29, Q33) %>%
  dplyr::mutate_all(as.character) %>%
  replace(.=="Normal Vision",0)%>%
  replace(.=="Corrected Vision", 0)%>%
  replace(.=="Non Corrected Vision", 1)%>%
  replace(.=="No, but I am fluent", .5)%>%
  dplyr::mutate(Q25 = replace(Q25, which(Q25 == "Yes"), 0))%>%
  dplyr::mutate(Q25 = replace(Q25, which(Q25 == "No"), 1))%>%
  dplyr::mutate(Q27 = replace(Q27, which(Q27 == "Yes"), 1))%>%
  dplyr::mutate(Q27 = replace(Q27, which(Q27 == "No"), 0))%>%
  dplyr::mutate(Q31 = replace(Q31, which(Q31 == "Yes"), 0))%>%
  dplyr::mutate(Q31 = replace(Q31, which(Q31 == "No"), 1))%>%
  dplyr::mutate_at(vars(starts_with("Q2")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)

#rename Questions about eligibility
data.Eligibility<-data.Eligibility %>%
  dplyr::rename(Elig_ColorBlindness=Q25,
         Elig_Dyslexic=Q27,
         Elig_NormalVision=Q29,
         Elig_NativeEnglish=Q31,
         Elig_YearsInUS=Q33)


```






## Demographic Information

```{r , echo=FALSE}
data.Demographic=data.filter %>%
  dplyr::select(SubID,PLATFORM,Q11,Q13,Q15,Q17,Q19,Q21,Q23) 

data.Demographic<-data.Demographic %>%
   dplyr::rename(Dem_Age=Q11,
         Dem_Sex=Q13,
         Dem_Gender=Q15,
         Dem_GenderOther=Q17,
         Dem_Ethnicity=Q19,
         Dem_EthDesc=Q21,
         Dem_Hispanic=Q23)
```




## STAI Y2

<!--Score Ranges = 1-4   S-Anxiety (Y1): Not at all = 1, Somewhat = 2, Moderately so = 3, Very much so = 4   T-Anxiety (Y2): Almost Never = 1, Sometimes = 2, Often = 3,Almost Always = 4  

S-Anxiety Reverse Coded Items: 1,2,5,8,10,11,15,16,19,20 T-Anxiety Reverse Coded Items: 21,23,26,27,30,33,34,36,39

STAI Sub Scales

State Anxiety (Y1): 1-20
Trait Anxiety (Y2): 21-40-->
```{r , echo=FALSE}

max_code=5


# Extract STAI items and reverse code
data.STAI=data.filter %>%
  dplyr::select(SubID,PLATFORM,starts_with("STAI_"))%>%
  dplyr::mutate_all(as.character) %>%
  replace(.=="Almost Never",1)%>%
  replace(.=="Sometimes",2)%>%
  replace(.=="Often",3) %>%
  replace(.=="Almost Always",4) %>%
  replace(.=="Prefer not to answer",NA) %>%
  dplyr::mutate_at(vars(-SubID,-PLATFORM), as.numeric) %>%
  mutate_at(.vars = vars(STAI_Y2_1,STAI_Y2_3,STAI_Y2_6,STAI_Y2_7,STAI_Y2_10,STAI_Y2_13,STAI_Y2_14,STAI_Y2_16,STAI_Y2_19), .funs = list(~max_code-.))  # this line does the reverse coding
  

```

## DASS depression subscale

<!-- Score Ranges = 0-3   Did not apply to me at all = 0
Applied to me to some degree, or some of the time = 1
Applied to me to a considerable degree, or a good part of time = 2
Applied to me very much, or most of the time = 3  

DASS Sub Scales

Depression: 3,5,10,13,16,17,21
Anxiety: 2,4,7,9,15,19,20
Stress: 1,6,8,11,12,14,18
To obtain scores, sum the scores. If 21 item scale, then multiply sum by 2-->

```{r , echo=FALSE}

data.DASS=data.filter %>%
  dplyr::select(SubID, PLATFORM,starts_with("DASS_")) %>%
  dplyr::mutate_all(as.character) %>%
  replace(.=="Did not apply to me at all",0) %>%
  replace(.=="Applied to me to some degree, or some of the time",1) %>%
  replace(.=="Applied to me to a considerable degree, or a good part of time",2) %>%
  replace(.=="Applied to me very much, or most of the time",3) %>%
  replace(.=="Prefer not to answer",NA) %>%
  dplyr::mutate_at(vars(-SubID,-PLATFORM), as.numeric)

```


## COVID19 Impact Scale

<!-- Scored on a 4 point scale --> 
<!-- Higher scores indicate higher disrutption due to covid --> 
<!-- No Change=0, Mild=1, Moderate=2, Severe=3 --> 
<!-- C19IS_19 is an open ended response-->


```{r , echo=FALSE}
# recode data
data.COVID19IS=data.filter %>%
  dplyr::select(SubID,PLATFORM,Q45,Q47,Q49,Q51,Q53,Q55,Q57,Q59) %>%
  dplyr::mutate_all(as.character) %>%
  replace(.=="Prefer not to answer",NA)%>%
  replace(.=="No change", 0)%>%
  mutate_all(funs(str_replace_all(., "[\r\n]", "")))%>%
  mutate_all(funs(str_replace(., ".*Severe.*", "3")))%>%
  mutate_all(funs(str_replace(., ".*Moderate.*", "2")))%>%
  mutate_all(funs(str_replace(., ".*Mild.*", "1")))%>%
  mutate_all(funs(str_replace(., ".*No Change.*", "0")))
  
  
```



## Merge data

```{r, echo=FALSE}


#merge all of the cleaned data files 

data.cleanSRMS <-data.duration %>%
  join(data.Eligibility,by=c("SubID","PLATFORM") ) %>%
  join(data.Demographic,by=c("SubID","PLATFORM") ) %>%
  join(data.DASS,by=c("SubID","PLATFORM") ) %>%
  join(data.STAI,by=c("SubID","PLATFORM") ) %>%
  join(data.COVID19IS,by=c("SubID","PLATFORM") )
 
write.csv(data.cleanSRMS,path.clean.data, row.names = FALSE)





```


