---
title: "SPICE_V_xxx_Debrief_Cleaning"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Clean Enviorment
```{r, echo=FALSE, warning=FALSE}

#Clear environemnt and Load Packages

# clear the environment
rm(list=ls()) 

#detach("package:here", unload = TRUE)

if (!require("pacman")) install.packages("pacman")
 pacman::p_load(
   plyr,  # For join function
   tidyverse, #for dyplr function
   stringr #for splitting string data
   )
```

#Set Working Directory and Paths 
```{r, echo=FALSE, warning=FALSE}

# Set Working Directory and Paths 
curDir=getwd()
## set directory 
setwd(curDir)
curDate=Sys.Date()
# import data

#CHANGE ONLY INFORMATION BELOW#
##------------##
#set version to current study version
curVersion="SPICE20200909"

#Change path to the raw data: change the file name after Raw/
path.raw.data= "../../../../Data/Qualtrics/Raw/SPICE-Debrief+Current_October+26,+2020_12.46.csv"

#only indluce if also doin prolific
#ProlificLogPath<-"../../../../Participants/Prolific/prolific_export_TCB_20200724.csv"

#Change path to the sona participant log: change the file name after Sona/

##------------##
SONA_PAYLogPath=paste0("../../../../Participants/",curVersion,"/SONA_PAY")
SONA_CREDITLogPath=paste0("../../../../Participants/",curVersion,"/SONA_CREDIT")


path.clean.data = paste("../../../../Data/Qualtrics/Clean/", curDate,"_SPICE_SRMS_Clean_Version_",curVersion,".csv", sep = "")

```

#Import Raw Data
```{r, echo=FALSE, warning=FALSE}

#import raw data


data.raw = read.csv(file = path.raw.data,header=TRUE,na.strings="")


Sona_PayFiles = list.files(path=SONA_PAYLogPath, pattern="*.csv", full.names=TRUE)
data.SonaPay = ldply(Sona_PayFiles, read_csv)

Sona_CreditFiles = list.files(path=SONA_CREDITLogPath, pattern="*.csv", full.names=TRUE)

data.SonaCredit = ldply(Sona_CreditFiles, read_csv)

```



#Filter Sona and Prolific Participant logs by Approved (PROLIFIC) and Participated (SONA)
<!--This does not yet filter out people who might have had errors or messaged the researcher-->

```{r, echo=FALSE, warning=FALSE}


if(length(data.SonaCredit!=0))(
data.SonaCredit.filter<- data.SonaCredit %>%
    dplyr::filter(credit_type=="Participated")%>%
    dplyr::select(survey_id)%>%
    distinct(survey_id)%>%
    rename(SubID=survey_id)

)

if(length(data.SonaPay!=0))(
data.SonaPay.filter<- data.SonaPay %>%
   dplyr::filter(credit_type=="Participated")%>%
    dplyr::select(survey_id)%>%
    distinct(survey_id)%>%
    rename(SubID=survey_id)
)
# 
# if(length(data.prolific!=0))(
# 
# data.prolific.filter<- data.prolific %>%
#    dplyr::select(participant_id,status)%>%
#    dplyr::filter(status=="APPROVED")%>%
#     dplyr::select(participant_id)%>%
#     distinct(participant_id)%>%
#     rename(SubID=participant_id)
# )
# 
# data.Independent<- data.raw%>%
#   filter(PLATFORM=="INDEPENDENT")%>%
#   select(INDEPENDENT_PID)%>%
#   distinct(INDEPENDENT_PID)%>%
#     rename(SubID=INDEPENDENT_PID)

data.SubjectListCombined<- join(data.SonaCredit.filter, data.SonaPay.filter,type= "full")
#data.SubjectListCombined<- join(data.prolific.filter, data.SonaPay.filter,type= "full")
#data.SubjectListCombined<- join(data.SubjectListCombined,data.Independent,type= "full")
```



#Filter Raw Data by Study Version
```{r, echo=FALSE, warning=FALSE}

data.filter<- data.raw %>%
   dplyr::filter(assignmentId==curVersion)

```


#Filter Raw Data by IDs in prolific and sona subject logs
```{r, echo=FALSE, warning=FALSE}

data.filter<- data.filter %>%
# dplyr::filter(workerId %in%data.prolific.filter$participant_id |SubID %in%data.Sona.filter$survey_id ) 
  dplyr::filter(workerId %in%data.SubjectListCombined$SubID ) 
```




## Embedded Data Information
```{r , echo=FALSE}
data.Embedded=data.filter %>%
  dplyr::select(workerId,PLATFORM, bG,bP,Group,order)

```



## Difficulty Cues
<!-- Scored on a 12 point scale -->

<!-- PosHigh_1:Like -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- PosHigh_2:Pleasant -5 unpleasant/negative = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 pleasant/positive= 5 Prefer not to respond =NA -->

<!-- PosHigh_3:Arousal -5 relaxed/calm = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 stimulated/aroused= 5 Prefer not to respond =NA -->

<!-- PosHigh_4:Motivation -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- PosHigh_5:Difficult -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- PosHigh_6:Effort -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->


<!-- PosHigh_7:Attention -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

### Low Difficulty Cue
```{r, echo=FALSE, warning=FALSE}

# recode data
data.PosHigh=data.filter %>%
  dplyr::select(workerId,PLATFORM,starts_with("Composite_Collector_PosLPenL"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("PosHigh_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.PosHigh<-data.PosHigh %>%
  rename(PosHigh_Like= PosHigh__1, #7
         PosHigh_Pleasant= PosHigh__2, #1
         PosHigh_Arousal= PosHigh__3, #2
         PosHigh_Motivation= PosHigh__4, #3
         PosHigh_Difficult= PosHigh__5, #4
         PosHigh_Effort= PosHigh__6, #5
         PosHigh_Attention= PosHigh__7) #6
  

  
```

### High Difficulty Cue
```{r, echo=FALSE, warning=FALSE}

# recode data
data.PosLow=data.filter %>%
  dplyr::select(workerId,PLATFORM,starts_with("Composite_Collector_PosLPenH"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("PosLow_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.PosLow<-data.PosLow %>%
  rename(PosLow_Like= PosLow__1, #Composite_Collector_PosLPenH_1
         PosLow_Pleasant= PosLow__2,
         PosLow_Arousal= PosLow__3,
         PosLow_Motivation= PosLow__4,
         PosLow_Difficult= PosLow__5,
         PosLow_Effort= PosLow__6,
         PosLow_Attention= PosLow__7)
  

  
```




## Feedback
<!-- Scored on a 12 point scale -->

<!-- Apple_1:Like -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Apple_2:Pleasant -5 unpleasant/negative = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 pleasant/positive= 5 Prefer not to respond =NA -->

<!-- Apple_3:Arousal -5 relaxed/calm = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 stimulated/aroused= 5 Prefer not to respond =NA -->

<!-- Apple_4:Motivation -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Apple_5:Difficult -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Apple_6:Effort -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->

<!-- Apple_7:Attention -5 Not at all = -5, -4=-4, -3=-3, -2=-2, -1=-1, 0 Neutral=0, 1=1,2=2,3=3,4=4,5 A lot= 5 Prefer not to respond =NA -->


### Easy Feedback 1
```{r, echo=FALSE, warning=FALSE}

# recode data
data.Apple=data.filter %>%
  dplyr::select(workerId,PLATFORM,starts_with("Apple_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("Apple_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.Apple <-data.Apple %>%
  rename(Apple_Like=Apple__1,
         Apple_Pleasant= Apple__2,
         Apple_Arousal= Apple__3,
         Apple_Motivation= Apple__4,
         Apple_Difficult= Apple__5,
         Apple_Effort= Apple__6,
         Apple_Attention= Apple__7)
  
```

### Easy Feedback 2
```{r, echo=FALSE, warning=FALSE}

# recode data
data.Peach=data.filter %>%
  dplyr::select(workerId,PLATFORM,starts_with("Peach_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("Peach_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.Peach <-data.Peach %>%
  rename(Peach_Like=Peach__1,
         Peach_Pleasant= Peach__2,
         Peach_Arousal= Peach__3,
         Peach_Motivation= Peach__4,
         Peach_Difficult= Peach__5,
         Peach_Effort= Peach__6,
         Peach_Attention= Peach__7)
  
```

### Hard Feedback1 
```{r, echo=FALSE, warning=FALSE}

# recode data
data.Pear=data.filter %>%
  dplyr::select(workerId,PLATFORM,starts_with("Pear_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("Pear_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.Pear <-data.Pear %>%
  rename(Pear_Like=Pear__1,
         Pear_Pleasant= Pear__2,
         Pear_Arousal= Pear__3,
         Pear_Motivation= Pear__4,
         Pear_Difficult= Pear__5,
         Pear_Effort= Pear__6,
         Pear_Attention= Pear__7)
  
```
### Hard Feedback 2
```{r, echo=FALSE, warning=FALSE}

# recode data
data.Lemon=data.filter %>%
  dplyr::select(workerId,PLATFORM,starts_with("Lemon_"))%>% # select the variables you would like to work with (Always ID)
  dplyr::mutate_all(as.character)%>% # turn into the data type into character
  replace(.=="-5  Not at all" ,-5)%>% #replace and recode
  replace(.=="-5  unpleasant/negative" ,-5)%>%
  replace(.=="-5  relaxed/calm" ,-5)%>%
  replace(.=="-4",-4)%>%
  replace(.=="-3",-3)%>%
  replace(.=="-2",-2)%>%
  replace(.=="-1",-1)%>%
  replace(.=="0  Neutral",0)%>%
  replace(.=="1",1)%>%
  replace(.=="2",2)%>%
  replace(.=="3",3)%>%
  replace(.=="4",4)%>%
  replace(.=="5  A lot" ,5)%>%
  replace(.=="5 pleasant/positive"  ,5)%>%
  replace(.=="5  stimulated/aroused",5)%>%
  dplyr::mutate_at(vars(starts_with("Lemon_")),as.numeric)%>% # turn into the data type into numeric
  replace(.=="Prefer not to respond",NA)


# rename variables to informative name
data.Lemon <-data.Lemon %>%
  rename(Lemon_Like=Lemon__1,
         Lemon_Pleasant= Lemon__2,
         Lemon_Arousal= Lemon__3,
         Lemon_Motivation= Lemon__4,
         Lemon_Difficult= Lemon__5,
         Lemon_Effort= Lemon__6,
         Lemon_Attention= Lemon__7)
  
```

